\textbf{CSDS 491: Assignment 4}

### 2021-04-21 A4/article.tex
🐛 💄 Fix typos in E1.
✨ Add answers to E1.

\section*{E1. Multivariate Gaussians}
\section*{E2. Linear Gaussian Models}

@@

We further know that there must be $p(y \mid x) = \mathcal N(\overline{\mu}, \overline{\mu})$, where:

@@

>>>>

\section*{E1. Multivariate Gaussians}

Please refer to \ilc{A4/code/e1.py} for the code implmentations of below plots.

\subsection*{1.1.}

For 2D multivariate normal we have $\Sigma = \qbm{\sigma_{xx} & \sigma_{xy} \\ \sigma_{yx} & \sigma_{yy}}$. Note:

\begin{itemize}
    \item For $x$ and $y$ to be uncorrelated, we have $\sigma_{xy} = \sigma_{yx} = 0$. For demo, we have $\mathcal N(\mu = \qbm{0 \\ 0}, \Sigma = \qbm{1 & 0 \\ 0 & 1})$.
    \item For $x$ and $y$ to be uncorrelated, we have $\sigma_{xy} = \sigma_{yx} > 0$. For demo, we have $\mathcal N(\mu = \qbm{0.5 \\ 0.5}, \Sigma = \qbm{1 & 0.9 \\ 0.9 & 1})$.
    \item For $x$ and $y$ to be anti-correlated, we have $\sigma_{xy} = \sigma_{yx} < 0$. For demo, we have $\mathcal N(\mu = \qbm{0.7 \\ 0.7}, \Sigma = \qbm{1 & -0.9 \\ -0.9 & 1})$.
\end{itemize}

\begin{figure}[H]
\minipage{0.3\textwidth}
  \includegraphics[width=\linewidth]{{fig/e1.1_1}.png}
  \caption*{Uncorrelated}
\endminipage\hfill
\minipage{0.3\textwidth}
    \includegraphics[width=\linewidth]{{fig/e1.1_2}.png}
    \caption*{Correlated}
\endminipage\hfill
\minipage{0.3\textwidth}
    \includegraphics[width=\linewidth]{{fig/e1.1_3}.png}
    \caption*{Anti-correlated}
\endminipage
\end{figure}

\subsection*{1.2.}

Assuming the same $\mu$ and $\Sigma$ setup in \textbf{Exercise 1.1}, we have the $1-, 2-, 3-\sigma$ countour plots being (note eigenvectors are scaled \ilc{4x} for visual purposes):

\begin{figure}[H]
\minipage{0.3\textwidth}
  \includegraphics[width=\linewidth]{{fig/e1.2_1}.png}
  \caption*{Uncorrelated}
\endminipage\hfill
\minipage{0.3\textwidth}
    \includegraphics[width=\linewidth]{{fig/e1.2_2}.png}
    \caption*{Correlated}
\endminipage\hfill
\minipage{0.3\textwidth}
    \includegraphics[width=\linewidth]{{fig/e1.2_3}.png}
    \caption*{Anti-correlated}
\endminipage
\end{figure}

\section*{E2. Linear Gaussian Models}

@@

We further know that there must be $p(y \mid x) = \mathcal N(\overline{\mu}, \overline{\Sigma})$, where:

@@

\section*{Exploration}

% https://www.youtube.com/watch?v=NEaUSP4YerM
% https://medium.com/@violante.andre/an-introduction-to-t-sne-with-python-example-47e6ae7dc58f
